Kernel Phase and Coronagraphy with Automatic Differentiation

### 2020-05-28 ms.tex
Updates from Overleaf

\begin{figure}
\plotone{kernel_modes_corona.pdf}
\caption{Some kernel phase maps - damped (nearly-singular) vectors in the image plane from the SVD of the coronagraph Jacobian in~\ref{speckle_jacobian}. There is little apparent structure in these except for weak patterns around the occulted region.
\label{kernel_corona}}
\end{figure}

>>>>

\begin{figure}
\plotone{kernel_modes_corona.pdf}
\caption{Some kernel speckle maps - damped (nearly-singular) vectors in the image plane from the SVD of the coronagraph Jacobian in~\ref{speckle_jacobian}. There is little apparent structure in these except for weak patterns around the occulted region.
\label{kernel_corona}}
\end{figure}
